### 2024-09-04 manuscript.tex
Improve code availability section

The ALCF, cl2nc, rstool, and our plotting code are open source and available at
\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc}, and
\url{https://github.com/peterkuma/rstool}, and
\url{https://github.com/peterkuma/icon-so-2024-code}, respectively. CyTRACK
is available at \url{https://github.com/apalarcon/CyTRACK}.

>>>>

The ALCF, cl2nc, rstool, lidar precipitation detection code, and our data
processing and plotting code are open source and available at
\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc}, and
\url{https://github.com/peterkuma/rstool}, and
\url{https://github.com/peterkuma/alcf-precip},
\url{https://github.com/peterkuma/icon-so-2024}, respectively. CyTRACK is
available at \url{https://github.com/apalarcon/CyTRACK}.
